Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta- analysis \thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2019-08-29 zhf_manuscript/zhf_manuscript.Rmd
prisma diagram

Sixteen studies were eligible for inclusion in this systematic review. 
>The characteristics of each study are in online supplementary [file 1](link to file 1).

@@

Table 1
|---|---|---|---|---|---|---|---|---|---|---|---|---|
|Table 1 Results of meta-analysis of agreement between transcutaneous and arterial carbon dioxide|
|---|---|---|---|---|---|---|---|---|---|---|---|---|
|---|Studies|N|n|Bias|SD|tau2|LoA_L|LoA_U|CI_L|CI_U|
|---|---|---|---|---|---|---|---|---|---|---|---|---|
|Subset|Stu-content|N-content|n-content|Bias-content|SD-content|tau2-content|LoAL-content|LoAU-content|CIL-content|CIU-content|
|Subset|Stu-content|N-content|n-content|Bias-content|SD-content|tau2-content|LoAL-content|LoAU-content|CIL-content|CIU-content|

Table 2
|Outcome|Summary accuracy and precision (C)|Participants|Study characteristics|Quality|Implications|
|---|---|---|---|---|---|
|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|
|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|
|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|
|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|

>>>>

Sixteen studies were eligible for inclusion in this systematic review (Figure 1).

```{r echo=FALSE, fig.height=4.5}
knitr::include_graphics("figure_one.png")
```

>The characteristics of each study are in online supplementary [file 1](link to file 1).

@@

### 2019-08-29 zhf_manuscript/zhf_manuscript.tex
prisma diagram

Core temperature monitoring is an important intervention within
perioperative and intensive care settings\((ref)\). Thermoregulatory
dysfunction is commonly associated with the induction of anesthesia and
can lead to adverse outcomes including cardiac dysrhythmias, altered
hemostasis and increased risk of surgical site infection (Frank et al.
1997; Kurz, Sessler, and Lenhardt 1996; Michelson et al. 1994; Rohrer
and Natale 1992). The pulmonary artery catheter is the reference
standard for continuous core temperature monitoring\((ref)\), however,
the invasive nature of this method renders an increased risk of
bloodstream infections and damage to surrounding tissue(Hadian and
Pinsky 2006). Although clinically accurate relative to pulmonary artery
thermometry, surrogate measures of core temperature via esophageal,
rectal, and bladder sites remain mildly invasive interventions\((ref)\).

@@

The agreement between ZHF and established core temperature measures has
been investigated in several studies conducted within the clinical
setting, each with varied results. Appraisal of these studies and
synthesis of the results would aid
\textbackslash{}\clinical {decision-making regarding the appropriate circumstances in which ZHF monitoring may be used.}

We aimed to determine if the ZHF sensor has clinically acceptable
accuracy and precision compared with established core temperature tools.
Accuracy is defined as the average difference between the ZHF sensor and
established core temperature instrument and precisions as the variance
(typically reported as the SD) in the differences.

@@

The selection of studies was undertaken by two independent reviewers.
Studies were included if reported measures from a ZHF sensor and another
established core temperature tool coincided. Studies involving a case
control design were excluded due to potential for overestimation of the
intervention performance. Studies were excluded if conducted on
non-human subjects or outside of a clinical healthcare setting. Studies
were excluded if conducted earlier than the year 2000 as prior studies
evaluated outdated technology that is no longer relevant to current
clinical practice.

@@

\begin{quote}
Information was extracted regarding study characteristics(author, year
of publication, country, design, sample size, clinical setting, numbers
studied and analyses for each outcome), population characteristics
(inclusion and exclusion criteria) and ZHF characteristics (timing and
methods of measurements, and methods of calibration).
\end{quote}

The outcomes that were extracted included the mean bias (eg, accuracy)
and variance (eg, SD, precision) in temperature between the ZHF sensor
and established core temperature measurement tool.
\textgreater{}Information was extracted about how repeated measurements
were handled: (1) analysed each pair of data separately; (2) treated
each pair of data as independent; or (3) used either analysis of
variance or a random effects model as a way to control for the dependent
nature of the repeated measures data (Myles and Cui 2007).

Using the revised Quality Assessment of Diagnostic Accuracy Studies
(QUADAS-2), each reviewer independently assessed the risk of bias for
the included studies (Whiting et al. 2011). \textgreater{}Reviewers used
guiding questions to rate the risk of bias for patient selection,

conduct of the ZHF measurements, conduct of the established core
temperature measurement tools, and timing and flow (eg, timing of ZHF
and established core temperature measurements, dropouts) as ``high'',
``low'' or ``unclear''. We worked to minimize the risk of publication
bias by conducting a comprehensive search of multiple databases as well
as an international clinical trial registry (Glasziou et al. 2001).
\textgreater{}Statistical analyses to detect reporting bias were not
conducted due to lack of validated methods (Begg 2005). Although some
meta-analyses of method comparison studies have used tests for detecting
funnel plot asymmetry (Niven et al. 2015), simulations have revealed
that such tests will result in publication bias being incorrectly
identified too often (Deeks, Macaskill, and Irwig 2005).

@@

The objective
\textgreater{}\(for the meta-analysis was to estimate the population limits of agreement between\)

temperature measurements by the ZHF sensor and established core
temperature measurement tools. \textgreater{}The framework for
meta-analysis of Bland-Altman method comparison studies based on limits
of agreement (LoA) approach was used (Tipton and Shuster 2017).

@@

and (2) repeated measurements were adjusted if improperly adjusted for
in \textgreater{}individual studies (by using weights proportional to
the number of samples, not the total number of measurements).

@@

Prior to conducting the meta-analyses, the results from each study were
converted into a standard format, with bias meaning \(ECT - ZHF\)
measured in \(^\circ C\). In two of the studies, the results were
reported for two separate groups of participants, so these were treated
in the meta-analyses as separate `studies'. \textgreater{}Other studies
reported separate results for analyses conducted using different TcCO2
device types or sensor locations performed on the same patients. Only
the result with the largest number of paired measurements between PaCO2
and TcCO2 was selected for inclusion in the main analysis, with others
included in subgroup meta-analyses where appropriate. For the studies
that reported results for patients while receiving both two-lung and
one-lung ventilation during thoracic surgery, we used the result for
two-lung ventilation in the main analysis. The conventionally cited
clinically acceptable agreement between

ECT and ZHF sensors is 0.5 \(^\circ C\)(ref).
\textgreater{}\(It was deemed that outer confidence bounds for 95\% LoA between ECT and ZHF (termed as ‘population limits of agreement’) outside of these bounds would\)

be clinically unacceptable. Sensitivity analysis for the primary
meta-analysis was performed based on risk of bias, whereby `unclear risk
of bias' was treated as `high risk' and `high risk of bias' studies were
excluded from analyses. \textgreater{}As clinicians would be interested
in the accuracy of

ZHF relative to thermometer devices they use, and within the clinical
setting in which they use it we conducted subgroup analyses according to
the comparator device used (eg, core, peripheral, nasopharangeal) and
clinical setting (eg, intraoperative, intensuve care unit).

@@

Sixteen studies were eligible for inclusion in this systematic review.
\textgreater{}The characteristics of each study are in online
supplementary \href{link\%20to\%20file\%201}{file 1}.

Using these studies, we conducted 6 different meta-analyses. The first
group compared ZHF to core (eg, arterial, bladder, esophageal, rectal)
temperature measurements and included 22 (73\%) comparisons from 14 (\%)
studies, and enrolled 607 participants with 179,821 paired measurements.
\textgreater{}The second group compared ZHF to core temperature
measurements in low risk bias studies studies that scored a low risk of
bias in all categories) and included 10 (\%) comparisons from 5 (\%)
studies, and enrolled 273 participants with 104,294 paired measurements.

The third group compared ZHF to core temperature measurements in ICU
patients and included 7 (23\%) comparisons from 5 (31\%) studies, and
enrolled 246 participants with 155,598 paired measurements. The fourth
group compared ZHF to core temperature measurement in intraoperative
patients and included 16 (53\%) comparisons from 10 (63\%) studies, and
enrolled 464 participants with 24,223 paired measurements. The fifth
group compared ZHF to nasopharyngeal temperature measurements and
included 4 (13\%) comparisons from 4 (25\%) studies, and enrolled 297
participants with 109,819 paired measurements. The sixth group compared
ZHF to sublingual temperature measurement and included 2 (7\%)
comparisons from 2 (13\%) studies, and enrolled 107 participants with
22731 paired measurements. The studies included in this systematic
review evaluated a ZHF temperature monitoring system manufactured by 3M.
Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF
device is now referred to as the Bair Hugger Temperature Monitoring
System. All comparisons reported adherence to the ZHF device
manufacturer instructions and placed the sensor on the forehead of the
participants. High risk of bias was associated with patient selection
for 13 (43\%) comparisons from 9 (56\%) studies, conduct of ZHF and
comparator measurements in 10(33\%) comparisons from 8 (50\%) studies
and 12 (40\%) comparisons 9 (30\%) studies, respectively (mostly due to
ZHF measurements being taken with knowledge of the comparator
measurements and vice versa) and participant flow for 13 (43\%) studies.
In 19 (50\%) comparisons from 8 (50\%) studies, the authors had declared
a conflict of interest or receipt of funding or equipment from the
manufacturer of the ZHF device under evaluation.

Table 1
\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}
\textbar{}Table 1 Results of meta-analysis of agreement between
transcutaneous and arterial carbon dioxide\textbar{}
\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}
\textbar{}---\textbar{}Studies\textbar{}N\textbar{}n\textbar{}Bias\textbar{}SD\textbar{}tau2\textbar{}LoA\_L\textbar{}LoA\_U\textbar{}CI\_L\textbar{}CI\_U\textbar{}
\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}
\textbar{}Subset\textbar{}Stu-content\textbar{}N-content\textbar{}n-content\textbar{}Bias-content\textbar{}SD-content\textbar{}tau2-content\textbar{}LoAL-content\textbar{}LoAU-content\textbar{}CIL-content\textbar{}CIU-content\textbar{}
\textbar{}Subset\textbar{}Stu-content\textbar{}N-content\textbar{}n-content\textbar{}Bias-content\textbar{}SD-content\textbar{}tau2-content\textbar{}LoAL-content\textbar{}LoAU-content\textbar{}CIL-content\textbar{}CIU-content\textbar{}

Table 2 \textbar{}Outcome\textbar{}Summary accuracy and precision
(C)\textbar{}Participants\textbar{}Study
characteristics\textbar{}Quality\textbar{}Implications\textbar{}
\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}
\textbar{}Out-content\textbar{}Sum-content\textbar{}Par-content\textbar{}Char-content\textbar{}Qual-content\textbar{}Impl-content\textbar{}
\textbar{}Out-content\textbar{}Sum-content\textbar{}Par-content\textbar{}Char-content\textbar{}Qual-content\textbar{}Impl-content\textbar{}
\textbar{}Out-content\textbar{}Sum-content\textbar{}Par-content\textbar{}Char-content\textbar{}Qual-content\textbar{}Impl-content\textbar{}
\textbar{}Out-content\textbar{}Sum-content\textbar{}Par-content\textbar{}Char-content\textbar{}Qual-content\textbar{}Impl-content\textbar{}

Table 3 \textbar{} test1 \textbar{} test2 \textbar{} test3 \textbar{}
test4 \textbar{} test5 \textbar{}
\textbar{}-------\textbar{}-------\textbar{}-------\textbar{}-------\textbar{}-------\textbar{}
\textbar{} a \textbar{} b \textbar{} c \textbar{} d \textbar{} e
\textbar{} \textbar{} a \textbar{} b \textbar{} c \textbar{} d
\textbar{} e \textbar{} \textbar{} a \textbar{} b \textbar{} c
\textbar{} d \textbar{} e \textbar{}

\# simple table creation here \textbar{} Tables \textbar{} Are
\textbar{} Cool \textbar{}
\textbar{}---------------\textbar{}:-------------:\textbar{}------:\textbar{}
\textbar{} col 3 is \textbar{} right-aligned \textbar{} \$1600
\textbar{} \textbar{} col 2 is \textbar{} centered \textbar{} \$12
\textbar{} \textbar{} zebra stripes \textbar{} are neat \textbar{} \$1
\textbar{}

>>>>

Core temperature monitoring is an important intervention within
perioperative and intensive care settings. Thermoregulatory dysfunction
is commonly associated with the induction of anesthesia and can lead to
adverse outcomes including cardiac dysrhythmias, altered hemostasis and
increased risk of surgical site infection (Frank et al. 1997; Kurz,
Sessler, and Lenhardt 1996; Michelson et al. 1994; Rohrer and Natale
1992). The pulmonary artery catheter is the reference standard for
continuous core temperature
monitoring\((ref - trouble finding a statement regarding this in the literature)\),
however, the invasive nature of this method renders an increased risk of
bloodstream infections and damage to surrounding tissue(Hadian and
Pinsky 2006). Although clinically accurate relative to pulmonary artery
temperature measurements, surrogate measures of core temperature at
esophageal, rectal, and bladder locations remain mildly invasive
interventions\((ref)\).

@@

The agreement between ZHF and established core temperature devices has
been investigated in several studies conducted within the clinical
setting, each with varied results. Appraisal of these studies and
synthesis of the results would aid clinicians in deciding the
appropriate circumstances in which ZHF may be used.

We aimed to determine if ZHF has clinically acceptable accuracy and
precision relative to established core temperature measurement devices.
Accuracy is defined as the average difference between temperature
measurements from the ZHF and comparator device and precisions as the
variance (typically reported as the SD) in the differences.

@@

The selection of studies was undertaken by two independent reviewers.
Studies were included if reported measures from a ZHF and comparator
device coincided. Studies involving a case control design were excluded
due to potential for overestimation of the intervention performance.
Studies were excluded if conducted on non-human subjects or outside of a
clinical healthcare setting. Studies were excluded if conducted earlier
than the year 2000 as prior studies evaluated outdated technology that
is no longer relevant to current clinical practice.

@@

Information was extracted regarding study characteristics (author, year
of publication, country, design, sample size, clinical setting, numbers
studied and analyses for each outcome), population characteristics
(inclusion and exclusion criteria) and ZHF characteristics (placement of
sensor, timing and methods of measurements). The outcomes that were
extracted included the mean bias (eg, accuracy) and variance (eg, SD,
precision) in temperature measurement between the ZHF sensor and
comparator device. \textgreater{}Information was extracted about how
repeated measurements were handled: (1) analysed each pair of data
separately; (2) treated each pair of data as independent; or (3) used
either analysis of variance or a random effects model as a way to
control for the dependent nature of the repeated measures data (Myles
and Cui 2007).

Using the revised Quality Assessment of Diagnostic Accuracy Studies
(QUADAS-2), each reviewer independently assessed the risk of bias for
the included studies (Whiting et al. 2011). Using guiding questions,
reviewers rated the risk of bias for patient selection, conduct of the
ZHF measurements, conduct of the comparator device measurements, and
timing and flow (eg, timing of ZHF and established core temperature
measurements, dropouts) as ``high'', ``low'' or ``unclear''. We worked
to minimize the risk of publication bias by conducting a comprehensive
search of multiple databases as well as an international clinical trial
registry (Glasziou et al. 2001). \textgreater{}Statistical analyses to
detect reporting bias were not conducted due to lack of validated
methods (Begg 2005). Although some meta-analyses of method comparison
studies have used tests for detecting funnel plot asymmetry (Niven et
al. 2015), simulations have revealed that such tests will result in
publication bias being incorrectly identified too often (Deeks,
Macaskill, and Irwig 2005).

@@

The objective for the meta-analysis was to estimate the population
limits of agreement between temperature measurements from the ZHF and
established comparator devices. \textgreater{}The framework for
meta-analysis of Bland-Altman method comparison studies based on limits
of agreement (LoA) approach was used (Tipton and Shuster 2017).

@@

and (2) repeated measurements were adjusted if improperly adjusted for
in \textgreater{}individual studies (by using weights proportional to
the number of participants, not the total number of measurements).

@@

Prior to conducting the meta-analyses, the results from each study were
converted into a standard format, with bias meaning \(comparator-ZHF\)
measured in \(^\circ C\). In several studies, results were reported for
multiple groups of participants, therefore in the meta-analysis each of
these groups was treated as a separate `comparison'. Other studies
reported multiple sets of results, whereby analyses were conducted
between ZHF and various comparator devices used on the same participant.
These instances were also treated as a separate `comparison' if the
comparator devices were apart of separate meta-analyses groups. One
study reported intraoperative, postoperative and overall results for the
same participants. Only the paired measurements from the overall results
were included in the main and low risk bias analyses, leaving paired
measurements exclusively from the intraoperative and postoperative
timepoints to be included in respective meta-analyses subgroups. The
conventionally cited clinically acceptable agreement between ZHF and
comparator devices is 0.5 \(^\circ C\)
\((ref - most of the studies site this range from Eshragi...)\).
\textgreater{}It was deemed that outer confidence bounds for 95\% LoA
between ECT and ZHF (termed as `population limits of agreement') outside
of these bounds would

be clinically unacceptable. Sensitivity analysis for the primary
meta-analysis was performed based on risk of bias, whereby `unclear risk
of bias' was treated as `high risk' and `high risk of bias' studies were
excluded from analyses. As clinicians would be interested in the
accuracy of ZHF relative to the thermometer devices they use, and within
the clinical setting in which they use it we conducted subgroup analyses
according to the comparator device used (eg, core, peripheral,
nasopharangeal) and clinical setting (eg, intraoperative, intensuve care
unit).

@@

Sixteen studies were eligible for inclusion in this systematic review
(Figure 1).

\includegraphics[width=53.08in]{figure_one}

\begin{quote}
The characteristics of each study are in online supplementary
\href{link\%20to\%20file\%201}{file 1}.
\end{quote}

Using these studies, we conducted 6 different meta-analyses. The first
group compared ZHF to core (eg, arterial, bladder, esophageal, rectal)
temperature measurements and included 22 (73\%) comparisons from 14 (\%)
studies, and enrolled 607 participants with 179,821 paired measurements.
The second group compared ZHF to core temperature measurements in low
risk bias studies studies that scored a low risk of bias in all
categories) and included 10 (\%) comparisons from 5 (\%) studies, and
enrolled 273 participants with 104,294 paired measurements. The third
group compared ZHF to core temperature measurements in ICU patients and
included 7 (23\%) comparisons from 5 (31\%) studies, and enrolled 246
participants with 155,598 paired measurements. The fourth group compared
ZHF to core temperature measurement in intraoperative patients and
included 16 (53\%) comparisons from 10 (63\%) studies, and enrolled 464
participants with 24,223 paired measurements. The fifth group compared
ZHF to nasopharyngeal temperature measurements and included 4 (13\%)
comparisons from 4 (25\%) studies, and enrolled 297 participants with
109,819 paired measurements. The sixth group compared ZHF to sublingual
temperature measurement and included 2 (7\%) comparisons from 2 (13\%)
studies, and enrolled 107 participants with 22731 paired measurements.
The studies included in this systematic review evaluated a ZHF
temperature monitoring system manufactured by 3M. Previously known as
the SpotOn Temperature Monitoring System, the 3M ZHF device is now
referred to as the Bair Hugger Temperature Monitoring System. All
comparisons reported adherence to the ZHF device manufacturer
instructions and placed the sensor on the forehead of the participants.
High risk of bias was associated with patient selection for 13 (43\%)
comparisons from 9 (56\%) studies, conduct of ZHF and comparator
measurements in 10(33\%) comparisons from 8 (50\%) studies and 12 (40\%)
comparisons 9 (30\%) studies, respectively (mostly due to ZHF
measurements being taken with knowledge of the comparator measurements
and vice versa) and participant flow for 13 (43\%) studies. In 19 (50\%)
comparisons from 8 (50\%) studies, the authors had declared a conflict
of interest or receipt of funding or equipment from the manufacturer of
the ZHF device under evaluation.
